### 2012-11-13 doc/progress_plan/report.tex
Added PDF conversion bit

\subsection{Prototyping/Pilot Studies}

\subsection{Subsequent Changes to Methodology}

>>>>

\subsection{Prototyping/Current Work}

\subsubsection{PDF Conversion}
Most scientific papers available on the internet are formatted as PDF
documents. However, Partridge uses and stores documents that use the CoreSC
schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
spike work was carried out to determine the feasibility of converting papers
published as PDF documents into XML documents. Townsendi et al(2009) liken converting
PDF to XML to ``converting hamburgers into cows," they go on to explain that
PDF documents do not contain any semantic data and documents lose much of their
explicit structure when they are formatted in this way \cite{Townsend2009}.
Therefore, to convert PDF documents into an NLP-friendly format, some
heuristics must be used to detect the document's structure.

A prototype script was written using a Python PDF extraction library called
PDFMiner (\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).
This toolkit already contains some heuristics about how to extract text from
PDF documents in a sane way\cite{pdfminer}. The script then used the NLTK
library to split the text into sentences and save the document in a CoreSC
compatible format for processing by SAPIENTA.

The script had limited success due to the high variation of formatting within
scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
a free service hosted by the university of manchester, could be used instead of
PDFMiner. PDFX's main advantage is that it uses a machine learning system to
guess PDF document structures more accurately than through the use of simple
Heuristics. With an adapted backend that sends PDFs for analysis using PDFX and
then splits the results using NLTK, the conversion script now has a much higher
success rate and will be used as a preprocessor for adding PDF  documents to
Partridge.

\subsubsection{Interface Design}

\subsubsection{System Processes}
